Not Smelly Enough: Learning What Bad Smells to Ignore

### 2016-08-11 Manuscript.tex
Updates from ShareLaTeX

\documentclass[final,twocolumn,5p]{elsarticle}
\usepackage{tikz}
  \def\firstcircle{(90:1.75cm) circle (2.5cm)}
  \def\secondcircle{(210:1.75cm) circle (2.5cm)}
  \def\thirdcircle{(330:1.75cm) circle (2.5cm)} 
\usepackage{comment}
\usepackage{framed,graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{bigstrut}
\usepackage{color}
\usepackage{graphics} 
\usepackage{eqparbox}
\usepackage{graphics}
\usepackage{colortbl} 
%\usepackage{times}
 \usepackage{mathptmx} \usepackage[scaled=.90]{helvet} \usepackage{courier}
\usepackage{balance}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
\definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}

@@

\title{Which ``Bad Smells'' Can Be Ignored?}

\author{Rahul Krishna\corref{cor1}\textsuperscript{a,}}
\ead{rkrish11@ncsu.edu}
\author{Tim Menzies\corref{cor1}\textsuperscript{a,}}
\ead{tim.menzies@gmail.com}
\author{Lucas Layman\textsuperscript{b}}
\ead{ llayman@cese.fraunhofer.org }
\cortext[cor1]{Corresponding author: Tel:+1-919-396-4143(Rahul)}
\address{\textsuperscript{a}Department of Computer Science, North Carolina State University, Raleigh, NC, USA\\
\textsuperscript{b}Fraunhofer CESE, College Park, USA}

\begin{abstract} 
{\bf Context: }The literature lists many bad smells that may be detrimental to a software system. But which are relevant to the current project and which can be ignored?
Developers, text books, and tools disagree on which bad smells are important. 
Further, it is unclear at what threshold values smell-related metrics
should trigger code improvement or preventative maintenance. Most studies do not offer {\em both} measurable metrics {\em and} a threshold for their proposed bad smells.

@@

\noindent
According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk of introducing errors}'' (our italics).
\end{quote}
The literature is divided on the merits of bad smells.
Much research endorses them to guide
code improvement (e.g., refactoring or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
lists dozens of papers on smell detection and repair tools.

Other papers cast doubt on the value of bad smells
as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
As we show in this paper,  
 tools, text books, and developers disagree on what bad smells
are important enough to hunt down and eliminate. Our findings
are consistent with other research suggesting that universal bad
smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
the Fowler text has 6434 references. A search  on {\em ``bad smell''programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.
Hence it is important to understand the value of
this popular topic.  
Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

To address this problem, we propose the XTREE
tool that uses: 
     \begin{itemize}
         \item A historical log of defects seen previously in the code;
         \item  Bad smells expressed in terms of the 
          metrics   in that log;
         \item Some proposed refactorings justified using those bad smells.
     \end{itemize}
Given that,  XTREE can determine which
  proposed refactorings are to be ignored
since they are not justifiable  
with respect to the history of the project. XTREE addresses four problems that  make it hard to  learn useful
bad smells for a particular project.

{\em PROBLEM \#1:} As discussed in the next section, programmer
  cognitive biases result in different
developers declaring that
bad smell X or Y is most important. 
 XTREE offers a way to assess the value of competing recommendations to address smell X vs. Y.

{\em PROBLEM \#2:} Not all bad smells can be fixed. 
When new code must
be combined with code from a third party, 
sometimes the constraints of that code 
lead unavoidably to bad smells violations (e.g.
developers might need to passed as a single closure a  very long method
to  a third-party GUI toolkit).   In this case,
a refactoring proposed to reduce that bad smell
may be irrelevant since it cannot be applied to this code base.

To address this problem, XTREE {\em reasons optimistically} to find the set
$R_0$ of refactorings that \textit{might} be useful (see \tion{rq} on optimistic reasoning).
The space of \textit{actually usable} refactorings is 
the subset $R_1 \subseteq R_0$.
If a developer's proposed refactoring $R_2$ is
not in $R_0$, then it cannot be in the usable
set $R_1$.  We show experimentally that XTREE
often recommends small subsets of
code metrics as useful guides for refactoring. Thus, we
can rule out some proposed refactorings
since many of those proposals fall outside of the space
useful refactorings ($R_0$) suggested by XTREE.

{\em PROBLEM \#3:}  
Shantnawi~\cite{Shatnawi10} warns most  studies do not offer
{\em both} a metric and a threshold for proposed bad smells. For example,  Darcy and Kemerer~\cite{darcy05}
discuss object-oriented (OO) design metrics that might defect bad smells (e.g. an excessive
depth of inheritance tree), but they do not define thresholds
for when the code starts to smell bad.  
Shatnawi~\cite{Shatnawi10}
and  Alves et al.~\cite{Alves2010} are rare cases where both metrics and thresholds are defined (see \tion{bst}).
However, their approaches do not explore the interconnections between sets of code metrics. This is important if sets of
code metrics have to be changed at the same time.
For example, it is not possible to refactor a
long method if several smaller ones without increasing
the coupling metrics of a class. 
More generally, we say that bad smell thresholds should be
{\em conjunctions} of metric+threshold pairs that need to be changed {\em together}.
Shatnawi~\cite{Shatnawi10}
and Alves et al. report {\em disjunctions} of multiple metrics+thresholds~\cite{Shatnawi10,Alves2010} without indicating how changes to these metrics are related.

@@

{\em PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
Refactored code cannot be assessed just by a rerun of the the test
suite (since refactorings are supposed to preserve behavior), and otherwise one must wait for new defect reports to evaluate the effect of refactoring changes on code.  
% waiting to observe 
% code refactorings is meant to
% preserve the behavior of the system (i.e. the same tests
% should pass before and after the refactoring). 
% Also, it many not be practical
%  to assessing refactorings by making the
% refactorings,  then seeing what happens to that code for the rest
% of the project. In a test-driven agile project, as
% SCRUM meetings change what stories are implemented next,
% the operational profile that lead to defects in the old
% code may not be repeated in future executions. 
To resolve this  problem, SE researchers such as 
Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
use a pair of systems: 
\begin{enumerate}
    \item One system to propose changes;
\item A separate system to assess
how defective is the code before and after some
refactoring.
\end{enumerate}
For the second system,
 Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
quality model~\cite{Bansiya02}.
A shortcoming of QMOOD
is that quality models learned from other projects
may perform poorly when applied to new projects~\cite{localvsglobal}.

To solve this fourth problem, this study  eschews
older quality models like QMOOD, we use
Random Forests~\cite{Breiman2001} to learn defect predictors
from OO code metrics.
Note that, unlilke QMOOD, such measurements 
  are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.

The rest of this paper is structured as follows. 
The next section
discusses the cognitive
biases that make developers disagree on the relevance of those bad smells to
their particular projects
(that discussion is our motivation for developing 
tools like XTREE). This is followed by a discussion
on various methods to learn thresholds for bad smells.
After evaluating those methods, we discuss various threats to
validity that threaten our conclusions.

\subsection{Contributions of this Paper }
The XTREE learner has not been reported
previously. 
The comparative analysis of XTREE
    versus previously published approaches to learning
    bad smell detectors shows
    that XTREE   rarely perfoms
      worse that the other approaches~\cite{Shatnawi10,Alves2010}
      and often is it   much better at proposing
      changes that reduce the expected
      number of of the defects. Further, the number
    of code metrics mentioned by XTREE is far
    fewer than other approaches, making it easier to validate refactorings proposed by
    developers. 
We
show here that XTREE is less verbose and offers better recommendations than the CD tool   developed previously with Borges~\cite{me12c}.
 The experimental rig
 used to comparatively assess
    XTREE is another novel contribution\footnote{tiny.cc/XTREE}. Using the design
    of that rig,
    other researchers could confirm/improve/refute
    the conclusions of this paper.

\section{Motivation}\label{sect:prelim}

@@

\section{Learning Bad Smell Thresholds}\label{sect:bst}
Research studies and tools (e.g., SonarQube~\cite{sq15}) leverage OO metrics as representatives for code smells, as we do in this study. In this section, we focus on determining thresholds for interpreting these metrics as ``bad smells'' or not.

The SE literature offers  two ways to 
learning bad smell thresholds.
One approach relies on 
{\em outlier statistics}~\cite{erni96,bender99}. This approach
has been used   by Shatnawi~\cite{Shatnawi10}, Alvenes et al.~\cite{Alves2010}
    and Hermans et al.~\cite{hermans15}.
    Another approach is 
    based on {\em cluster deltas} that we developed
    for   Centroid Deltas~\cite{me12c} and 
    use here for XTREE. 
    These two approaches are discussed below.
\subsection{  Outlier Statistics}\label{sect:p}

@@

@@

\subsubsection{Discussion }\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction} problem.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what
metrics need to be changed at the same time.

@@

\subsubsection{CD}
Borges and Menzies first proposed the CD centroid delta approach to
generate {\em conjunctions} of code metrics
that need to be changes at the same time
in order to reduce defects~\cite{me12c}.
CD used the WHERE clustering algorithm developed by the
authors for a prior application~\cite{localvsglobal}.
Each cluster was then replaced by its centroid
and $\Delta$ was calculated directly from the difference
between code metrics values between one centroid
and its nearest neighbor.

>>>>

uu \documentclass[final,twocolumn,5p]{elsarticle}
\usepackage{tikz}
  \def\firstcircle{(90:1.75cm) circle (2.5cm)}
  \def\secondcircle{(210:1.75cm) circle (2.5cm)}
  \def\thirdcircle{(330:1.75cm) circle (2.5cm)} 
\usepackage{comment}
\usepackage{framed,graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{bigstrut}
\usepackage{color}
\usepackage{graphics} 
\usepackage{eqparbox}
\usepackage{graphics}
\usepackage{colortbl} 
%\usepackage{times}
 \usepackage{mathptmx} \usepackage[scaled=.90]{helvet} \usepackage{courier}
\usepackage{balance}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
\definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}

@@

\title{Not Smelly Enough:  Learning What Bad Smells to Ignore}

\author{Rahul Krishna\corref{cor1}\textsuperscript{a,}}
\ead{rkrish11@ncsu.edu}
\author{Tim Menzies\corref{cor1}\textsuperscript{a,}}
\ead{tim.menzies@gmail.com}
\author{Lucas Layman\textsuperscript{b}}
\ead{ llayman@cese.fraunhofer.org }
\cortext[cor1]{Corresponding author: Tel:+1-919-396-4143(Rahul)}
\address{\textsuperscript{a}Department of Computer Science, North Carolina State University, Raleigh, NC, USA\\
\textsuperscript{b}Fraunhofer CESE, College Park, USA}
\pagestyle{arabic}

\begin{abstract} 
{\bf Context: }The SE literature lists many  reasons
for reorganizing software projects; e.g. long methods are more bug prone
so it is wise to refactoring
very large methods into numerous smaller ones.
At least some of those recommendations are outdated (based on older projects)
or irrelevant (based on other projects). Yet developers persist
is following much of that advice, without critical reviewing
its relevance to the current project.

{\bf Objective:} If a developer is doing some task for reason ``X'', 
how can that developer's manager assess if ``X'' is a good reason
that justifies that task?

{\bf Method:} For a particular task (manual refactoring of code in order
to remove a bad smell), we check   if there is any historical evidence
to endorse that refactoring.  Ysing the XTREE

bad smells that may be detrimental to a software system. But which are relevant to the current project and which can be ignored?
Developers, text books, and tools disagree on which bad smells are important. 
Further, it is unclear at what threshold values smell-related metrics
should trigger code improvement or preventative maintenance. Most studies do not offer {\em both} measurable metrics {\em and} a threshold for their proposed bad smells.

@@

\noindent
``Managing people is like herding cats'', says management consultant Watler
Bennis~\cite{bennis97}. Nowhere is this more true than when managing programmers. 
Programmers can be very intelligent, but very opinionated people whose
social position within software organizations relies, in part,
of perceived notions of technical excellence. Hence, it can
be hard for managers to monitor and guide programmers away from wasting
time on nonproductive activity, particularly if that programmer can find
some support for that activity somewhere in the SE literature.

Consider, for example, the activity of refactoring code based on bad smells.
According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk 
of introducing errors}'' (our italics).
\end{quote}
The advice on what  bad smells to fix is extensive and, as we show below,
contradictory (see \fig{smells}) and poorly supported. Yet
programmers often use the SE literature to justify extensive refactoring efforts.
For example, this paper began when a Washington-based software company shared
one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. This management team wanted some way to check if all that activity was useful (hence, this article).

Note that these managers are {\em not} asking for better
automatic refactoring
tool support. Their human programmers are refactoring
code all the time, perhaps too much so.
Hence, their management goal is: 
\bi
\item
{\em Not} to optimize {\em necessary} refactorings;
\item
But rather to discourage {\em unnecessary} refactorings.
\ei
For those managers, we offer the  following heuristic:
\bi
\item If there is no evidence in the historical record that changing ``X'' is useful;
\item Then discourage developers from doing ``X''.
\ei
This paper describes one way to operationalize this heuristic, in the context
of assessing bad smells. We use data mining to generate two oracles: a {\em primary
change oracle} and a {\em secondary validation oracle}.
By combining these two oracles,
 we can generate and validate useful
changes to code modules.

In this paper, we use 
the XTREE cluster delta algorithm as the {\em primary change  oracle} .
XTREE 
explores the historical record of a project to find clusters of projects.
It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects$C_1$ (so $\Delta$
is some subset of $C_1 - C_0$). To define ``minimal'', XTREE uses an entropy measure.

As to 
the {\em secondary validation oracle}, this  checks if the primary oracle is proposing
sensible changes. For this purpose we  use Random Forests\cite{XXX}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{YYY}).
 In our framework,  learning
the secondary oracle is   a {\em separate} task to learning the primary
oracle. This  ensures that the validation oracle offers an independent
opinion on the value of the proposed changes.

When these oracles were applied to defect data from
open source object-oriented software systems, we discovered a {\em disjunctive fallacy}
in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.

\bi
\item A common heuristic is to recommend refactoring of a code module if any static
code measure grow ``unusually  large''
(see \tion{bst} for   different ways to defining ``unusually large'').
\item This can lead to a {\em disjunctive recommendation}; i.e. given knowledge
that some static
code measures $a_i$ is ``unusually large'' after some threshold $t_i$,
then refactor code if we ever the see disjunction:
\[\left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee \left(a_3 > t_3 \right)\bigvee   ...\]
\ei
This disjunctive recommendation is a fallacy.
According to XTREE's results,
there exists an intricate set of associations between static code measures
such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
It is easy to see why this is so.
A requirement for  refactoring is that the new code supports the same functionality
as before. If we pull code out of a function (since that function has grown too
large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
recommendation is that if we decrease a module's lines of code  then in the refactored
code, the functionality is achieved via a communication between several different parts
of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
that module's coupling metrics.

The XTREE results  confirmed the intuitions
of the project managers that prompted this investigation:
Yes,  indeed, their programmers
were wasting time on   performing refactorings  that  decreased multiple measures when, in fact,
they should be trying to {\em decrease} some measures while {\em increasing} others.
Also, in a study of five different JAVA OO systems,
XTREE found that  only $\frac{4}{20}=20$\% 
  of the measures were usually found within  change recommendations. That is, it is unlikely
  that refactoring based on measurements of  80\% of the code measures would be useful.

Based on the above, we recommend the use of XTREES as follows XXX

  The rest of this paper offers details on this study.  
  %YYYstructure of paper written here

  In order to support dissemination
  of research results, and to encourage other researchers to repeat our results,
  all the code used in this paper is publicly available\footntote{XXX: need a public repo}.

  \subsection{Relationship to Prior Work }
A four page prelininary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies only two  of
the eight data sets studied here. Also, that prior work had
no comparison to any baseline
method from other researchers, whereas this paper compares XTREE's recommendations
with those found by researchers exploring bad smells.
Also, that paper offered
no secondary oracle, i.e. no way to check if XTREE's recommended changes were sensible.
Further, syntactically, we note that this report is four times longer than that prior paper.

XXX next text here on CD

\section{Background}
\subsection{About Bad Smells}

Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.
Hence it is important to understand the value of
this popular topic.  
Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

The literature is divided on the merits of bad smells.
Much research endorses them to guide
code improvement (e.g., refactoring or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
lists dozens of papers on smell detection and repair tools. 
Yet
other papers cast doubt on the value of bad smells
as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
As we show in this paper,  
 tools, text books, and developers disagree on what bad smells
are important enough to hunt down and eliminate. Our findings
are consistent with other research suggesting that universal bad
smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

In our view, there are four major problems with bad smells.

{\bf PROBLEM \#1:} As discussed in the next section, programmer
  cognitive biases result in different
developers declaring that
bad smell X or Y is most important. 
 XTREE is useful for  assessing the relative importance of
   X vs. Y.

{\bf PROBLEM \#2:} Not all bad smells can be fixed. 
When new code must
be combined with code from a third party, 
sometimes the constraints of that code 
lead unavoidably to bad smells violations (e.g.
developers might need to passed as a single closure a  very long method
to  a third-party GUI toolkit).   In this case,
a refactoring proposed to reduce that bad smell
may be irrelevant since it cannot be applied to this code base.

Hence, XTREE {\em reasons optimistically} to find the set
$R_0$ of refactorings that \textit{might} be useful (see \tion{rq} on optimistic reasoning).
The space of \textit{actually usable} refactorings is 
the subset $R_1 \subseteq R_0$.
If a developer's proposed refactoring $R_2$ is
not in $R_0$, then it cannot be in the usable
set $R_1$.  We show experimentally that XTREE
often recommends small subsets of
code metrics as useful guides for refactoring. Thus, we
can rule out some proposed refactorings
since many of those proposals fall outside of the space
useful refactorings ($R_0$) suggested by XTREE.

{\bf PROBLEM \#3:}  
Shantnawi~\cite{Shatnawi10} warns most  studies do not offer
{\em both} a metric and a threshold for proposed bad smells. For example,  Darcy and Kemerer~\cite{darcy05}
discuss object-oriented (OO) design metrics that might defect bad smells (e.g. an excessive
depth of inheritance tree), but they do not define thresholds
for when the code starts to smell bad.  
Shatnawi~\cite{Shatnawi10}
and  Alves et al.~\cite{Alves2010} are rare cases where both metrics and thresholds are defined (see \tion{bst}).
However, their approaches do not explore the interconnections between sets of code metrics. This is important if sets of
code metrics have to be changed at the same time.
For example, it is not possible to refactor a
long method if several smaller ones without increasing
the coupling metrics of a class. 
More generally, we say that bad smell thresholds should be
{\em conjunctions} of metric+threshold pairs that need to be changed {\em together}.
Shatnawi~\cite{Shatnawi10}
and Alves et al. report {\em disjunctions} of multiple metrics+thresholds~\cite{Shatnawi10,Alves2010} without indicating how changes to these metrics are related.

@@

{\bf PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
Refactored code cannot be assessed just by a rerun of the the test
suite (since refactorings are supposed to preserve behavior), and otherwise one must wait for new defect reports to evaluate the effect of refactoring changes on code.  
% waiting to observe 
% code refactorings is meant to
% preserve the behavior of the system (i.e. the same tests
% should pass before and after the refactoring). 
Also, it many not be practical
 to assessing refactorings by making the
refactorings,  then seeing what happens to that code for the rest
of the project. In a test-driven agile project, as
SCRUM meetings change what stories are implemented next,
the operational profile that lead to defects in the old
code may not be repeated in future executions.

To resolve this  problem, SE researchers such as 
Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
use a pair of oracles: 
\begin{enumerate}
    \item A {\em primary oracle} system to propose changes;
\item A {\em secondary validation oracle} (which is learned separately
to the primary oracle) that   assesses
how defective is the code before and after some
refactoring.
\end{enumerate}
For the second system,
 Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
quality model~\cite{Bansiya02}.
A shortcoming of QMOOD
is that quality models learned from other projects
may perform poorly when applied to new projects~\cite{localvsglobal}.
Hence, for this study, we  eschew
older quality models like QMOOD. Instead, we use
Random Forests~\cite{Breiman2001} to learn defect predictors
from OO code metrics.
Note that, unlilke QMOOD, such measurements 
  are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.

\subsection{Why Not Just Ask Developers to Rank Bad Smells?}\label{sect:prelim}

@@

\section{Learning Bad Smell Thresholds}\label{sect:bst}

The SE literature offers  two ways to 
learning bad smell thresholds.
One approach relies on 
{\em outlier statistics}~\cite{erni96,bender99}. This approach
has been used   by Shatnawi~\cite{Shatnawi10}, Alvenes et al.~\cite{Alves2010}
    and Hermans et al.~\cite{hermans15}.
    Another approach is 
    based on {\em cluster deltas} that we developed
    for   Centroid Deltas~\cite{me12c} and 
    use here for XTREE. 
    These two approaches are discussed below.

@@

\subsection{Outlier Statistics}

@@

\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction} problem.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what
metrics need to be changed at the same time.

@@

\subsubsection{CD}\label{sec:cdcd}
Borges and Menzies first proposed the CD centroid delta approach to
generate {\em conjunctions} of code metrics
that need to be changes at the same time
in order to reduce defects~\cite{me12c}.
CD used the WHERE clustering algorithm developed by the
authors for a prior application~\cite{localvsglobal}.
Each cluster was then replaced by its centroid
and $\Delta$ was calculated directly from the difference
between code metrics values between one centroid
and its nearest neighbor.
